Cannibalism among the supermassive black holes

### 2018-10-16 paper.tex
Modified Merger Tree Data and Stellar Mass Adjustments Sections

\documentclass[english, apj]{emulateapj}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{rotating}
\usepackage{units}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsbsy}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{url}
\usepackage{babel}
\usepackage{float}
%\usepackage{siunitx}
%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}

@@

The above criteria narrowed the field of eligible galaxies down to 51.  In considering time and resources, we chose the top 13 galaxies in terms of number of black holes to run the simulations.  These black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.

@@

>>>>

\documentclass[english, apj]{emulateapj}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{rotating}
\usepackage{units}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsbsy}
\usepackage{amstext}
\usepackage{graphicx}
\usepackage{url}
\usepackage{babel}
\usepackage{float}
\usepackage{siunitx}
%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}
\usepackage[all]{hypcap}

@@

The above criteria narrowed the field of eligible galaxies down to 51.  In considering time and resources, we chose the top 13 galaxies in terms of number of black holes to run the simulations.  The black holes in these galaxies accounted for nearly $84{\%}$ of all orbiting black holes across all the galaxies, so it represented a reasonable balance between completeness and efficiency.

@@

\begin{table}[ht]
\centering
\caption{Galaxy characteristics at z=0}
\begin{tabular} {|c | c | c|}
\hline
$M_{*}$ & $M_{DM}$ & $M_{CBH}$ \\
\hline
\num{1.75e13} & \num{9.18e13} & \num{2.19e9} \\ 
\num{1.52e13} & \num{7.75e13} & \num{5.27e9} \\
\num{4.46e12} & \num{2.29e13} & \num{1.22e9} \\
\num{5.58e12} & \num{2.85e13} & \num{1.46e9} \\
\num{2.32e12} & \num{1.18e13} & \num{3.62e9} \\
\num{1.96e12} & \num{1.03e13} & \num{9.85e9} \\
\num{4.80e12} & \num{2.48e13} & \num{2.40e9} \\
\num{1.62e12} & \num{8.56e12} & \num{6.86e9} \\
\num{1.74e12} & \num{8.92e12} & \num{5.60e9} \\
\num{1.23e12} & \num{6.29e12} & \num{1.22e9} \\
\num{1.72e12} & \num{6.94e12} & \num{2.02e9} \\
\num{1.95e12} & \num{1.00e13} & \num{9.32e9} \\
\num{5.52e11} & \num{1.84e12} & \num{2.21e9} \\
\hline
\end{tabular}
\label{table:gal_char}
\end{table}
